### 2018-03-15 paper/4-build.tex
Revise as discussed

\todo{SLPJ}{What does this para add?}
Let \hs{result}~\hs{=}~\hs{build}~\hs{task}~\hs{key}~\hs{store}. The build
system \hs{build} is responsible for ensuring that \hs{key} and its dependencies
are up-to-date in \hs{result} starting from \hs{store} (\S\ref{sec-build-correctness}). As part of that work,
\hs{build} \emph{may} store auxiliary information \hs{info} of type \hs{i} in
the \hs{store}, which will be provided to future calls of \hs{build}.

@@

We assume that \hs{Hash} is a small constant size, constructed from hashing the
underlying \hs{v} rather than storing it directly. Checking a trace requires
ensuring all the dependencies are up-to-date (using whatever ordering strategy
as per \S\ref{sec-dependency-orderings}), then comparing if the dependencies are
same as the current value and that the result is the same. After computing a
fresh value we add its \hs{Trace} to the list. Therefore the information stored
by a build system that verifies traces is \hs{[Trace k v]}.

>>>>

\todo{SLPJ}{What does this para add?}
Let \hs{result}~\hs{=}~\hs{build}~\hs{task}~\hs{key}~\hs{store}. The build
system \hs{build} is responsible for ensuring that \hs{key} and its dependencies
are up to date in \hs{result} starting from \hs{store} (\S\ref{sec-build-correctness}). As part of that work,
\hs{build} \emph{may} store auxiliary information \hs{info} of type \hs{i} in
the \hs{store}, which will be provided to future calls of \hs{build}.

@@

We assume that \hs{Hash} is a small constant size, constructed from hashing the
underlying \hs{v} rather than storing it directly. Checking a trace requires
ensuring all the dependencies are up to date (using whatever ordering strategy
as per \S\ref{sec-dependency-orderings}), then comparing if the dependencies are
same as the current value and that the result is the same. After computing a
fresh value we add its \hs{Trace} to the list. Therefore the information stored
by a build system that verifies traces is \hs{[Trace k v]}.
